A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-07 ms.Rmd
cleaning TableS1

@@

```{r Figure S1, echo=FALSE, fig.cap="A correlation plot for the continuous variables used in the modelling procedures."}
knitr::include_graphics("figures/corrplot_of_continuous_variables.pdf")
```

```{r Figure S2, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("figures/accounting_for_phylo_uncertainty.pdf")
```

# Supplementary tables
```{r Table S1, echo=FALSE, fig.cap="Variance inflation factors for the explanatory variables used in the analysis."}
knitr::include_graphics("tables/collinearity_investigation.pdf")
```

>>>>

# Tables
```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
Table1 <- read_csv("Data/Table1.csv")

library(kableExtra)

kable(Table1, format = "latex", caption = "Results showing the significance of the phylogenetic signal analyses.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

```

@@

```{r Figure S1, echo=FALSE, fig.cap="A correlation plot for the continuous variables used in the modelling procedures."}
knitr::include_graphics("finalFigs/FigureS1.pdf")
```

```{r Figure S2, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("finalFigs/FigureS2.pdf")
```

# Supplementary tables
```{r Table S1, echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)

collinearity_investigation <- read_csv("Data/TableS1.csv")
collinearity_investigation <- collinearity_investigation[-1,]

kable(collinearity_investigation, format = "latex", caption = "Variance inflation factors for the explanatory variables used in the analysis.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

```

```{r Table S2, echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)

TableS2 <- read_csv("Data/TableS2.csv")

kable(TableS2, format = "latex", caption = "Summary statistics of the phylogenetic signal analysis.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))
```
